---
title: "flight_delay"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flight_delay}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LinearRegPackage)
library(nycflights13)
library(caret)
library(dplyr)
```

# Predictive modeling of flight delays using ridgereg()

1. In the first step, we create a new field - delay which is the sum of dep_delay
and arr_delay in the nycflights13::flights data. Consider only those entries
where delay is more than 0. Then join the flight data with the weather data to 
get the final set of dependent and independent variables.
```{r echo=TRUE, eval=TRUE}
flight_data <- dplyr::rowwise(nycflights13::flights) %>%
  dplyr::mutate(.,delay = sum(dep_delay, arr_delay, na.rm = T)) %>%
  dplyr::filter(., delay > 0) %>%
  dplyr::inner_join(., nycflights13::weather, 
                     by = c("origin", "year", "month", "day", "hour")) %>%
  dplyr::select(.,
                carrier,
                tailnum,
                origin,
                dest,
                month,
                day,
                flight,
                dep_time,
                arr_time,
                air_time,
                distance,
                delay,
                temp,
                humid,
                wind_dir,
                wind_speed,
                precip,
                visib)
head(flight_data)
```

2. In the next step, we convert the categorical data to integers for better precision
```{r echo=TRUE, eval=TRUE}
flight_data$carrier <- as.factor(flight_data$carrier)
flight_data$origin <- as.factor(flight_data$origin)
flight_data$dest <- as.factor(flight_data$dest)
flight_data$tailnum <- as.factor(flight_data$tailnum)
flight_data[,c('carrier', 'origin', 'dest', 'tailnum')] <- 
  sapply(flight_data[,c('carrier', 'origin', 'dest' , 'tailnum')], unclass)
head(flight_data)
```

3. Remove the entries with NA values
```{r echo=TRUE, eval=TRUE}
names(which(colSums(is.na(flight_data))>1))
flight_data <- na.omit(flight_data)
names(which(colSums(is.na(flight_data))>1))
```