---
title: "Predictive modelling for flight delays"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flight_delay}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LinearRegPackage)
library(nycflights13)
library(caret)
library(dplyr)
```

# Predictive modeling of flight delays using ridgereg()

1. In the first step, we create a new field - delay which is the sum of dep_delay
and arr_delay in the nycflights13::flights data. Consider only those entries
where delay is more than 0. Then join the flight data with the weather data to 
get the final set of dependent and independent variables.
```{r echo=TRUE, eval=TRUE}
set.seed(2)
flight_data <- dplyr::rowwise(nycflights13::flights) %>%
  dplyr::mutate(.,delay = sum(dep_delay, arr_delay, na.rm = T)) %>%
  dplyr::filter(., delay > 0) %>%
  dplyr::inner_join(., nycflights13::weather, 
                     by = c("origin", "year", "month", "day", "hour")) %>%
  dplyr::select(.,
                carrier,
                tailnum,
                origin,
                dest,
                month,
                day,
                flight,
                dep_time,
                arr_time,
                air_time,
                distance,
                delay,
                temp,
                humid,
                wind_dir,
                wind_speed,
                precip,
                visib)
head(flight_data)
```

2. In the next step, we convert the categorical data to integers for better precision
```{r echo=TRUE, eval=TRUE}
flight_data$carrier <- as.factor(flight_data$carrier)
flight_data$origin <- as.factor(flight_data$origin)
flight_data$dest <- as.factor(flight_data$dest)
flight_data$tailnum <- as.factor(flight_data$tailnum)
flight_data[,c('carrier', 'origin', 'dest', 'tailnum')] <- 
  sapply(flight_data[,c('carrier', 'origin', 'dest' , 'tailnum')], unclass)
head(flight_data)
```

3. Remove the entries with NA values
```{r echo=TRUE, eval=TRUE}
names(which(colSums(is.na(flight_data))>1))
flight_data <- na.omit(flight_data)
names(which(colSums(is.na(flight_data))>1))
```

4. Next split the data into training, validation and test.
```{r echo=TRUE, eval=TRUE}
training_index <- caret::createDataPartition(flight_data$delay, p=0.95, list = F)
data_test <- flight_data[-training_index,]
validation_index <- createDataPartition(flight_data$delay[training_index], 
                                        p=0.16, list = F)
data_validation <- flight_data[validation_index,]
data_train <- flight_data[-validation_index,]
dim(data_train)
dim(data_validation)
dim(data_test)
```

5. Pre-process the data: scale and center the values for better precision
```{r echo=TRUE, eval=TRUE}
preProcValues <- preProcess(flight_data[,c(
  'dep_time',
  'arr_time',
  'air_time',
  'distance',
  'delay',
  'temp',
  'humid',
  'wind_dir',
  'wind_speed',
  'precip',
  'visib'
  )], method = c("center", "scale"))
data_train <- predict(preProcValues, data_train)
data_validation <- predict(preProcValues, data_validation)
data_test <- predict(preProcValues, data_test)
```

6. Train the model with different lambda values. For each lambda value, evaluate the model
against the validation data set. We consider the lamda values from 1 to 50.
```{r echo=TRUE, eval=TRUE}
final_df <- data.frame(matrix(nrow=0,ncol=4))
colnames(final_df) <- c('lambda',
                        'RMSE',
                        'RSQ',
                        'MAE')
coef_df <- NULL
for (i in 1:50) {
  robj <- ridgereg$new(formula = delay~., 
                           data = data_train, 
                           lambda = i)  
  x_pred <- robj$predict(data_validation)
  perf_ridge <- postResample(pred = x_pred, obs = data_validation$delay)
  final_df <- rbind(final_df, data.frame(lambda=i,
                               RMSE=perf_ridge[1],
                               RSQ=perf_ridge[2],
                               MAE=perf_ridge[3]))
  coef <- c(lambda = i,robj$beta_ridge)
  coef_df <- rbind(coef_df, t(as.data.frame(coef)))
}
rownames(final_df) <- NULL
```

7. Plotting the RMSE, RSQ & MAE graphs
a. RMSE
```{r echo=TRUE, eval=TRUE}
ggplot(final_df) + geom_line(aes(x=lambda, y= RMSE))
```

b. MAE
```{r echo=TRUE, eval=TRUE}
ggplot(final_df) + geom_line(aes(x=lambda, y= MAE))
```

c. RSQ
```{r echo=TRUE, eval=TRUE}
ggplot(final_df) + geom_line(aes(x=lambda, y= RSQ))
```

8. The optimal lambda value here is:
```{r echo=TRUE, eval=TRUE}
final_df[final_df$RMSE == min(final_df$RMSE),]
opt_lambda <- final_df[final_df$RMSE == min(final_df$RMSE),]$lambda
```

9. Using the optimal lambda value, predict the test data
```{r echo=TRUE, eval=TRUE}
robj <- ridgereg$new(formula = delay~., 
                           data = data_test, 
                           lambda = opt_lambda)  
x_pred <- robj$predict(data_test)
perf_ridge <- postResample(pred = x_pred, obs = data_test$delay)
perf_ridge
```