---
title: "LinearRegVignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{LinearRegVignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LinearRegPackage)
```

This is a package to handle linear regression models. We use it to calculate the various computation required for multiple linear regression and also offer certain functions like plot, print etc.

# Classes offered by the package
1. **linreg**: linreg class contains the following attributes:
    * formula of 'formula' type: Contains the formula passed by the user
    * data of 'data.frame' type: Contains the data passed by the user
    * est_beta of 'vector' type: Regression coefficient calculated by the class
    * y_pred of 'matrix' type: Fitted Values calculated by the class
    * resid_e of 'matrix' type: Residual calculated by the class
    * deg_freed of 'numeric' type: Degrees of Freedom calculated by the class
    * resid_var_e of 'matrix' type: Residual Variance caclculated by the class
    * var_est_beta of 'vector' type: Variance of Regression Coefficient calculated by the class
    * t_val_beta of 'matrix' type: T-value for each coefficient
    * data_set of 'character' type

    To create an object of class linreg, the formula and data
    attributes must be passed. An example is shown below:
    
    ```r
    linreg$new(Petal.Length~Sepal.Width+Sepal.Length, data=iris)
    ```
    This will create a new object of the linreg class with all the above mentioned computations.
    
## Methods offered by the class
1. print()  

    This method prints out the $\hat{\beta}$, that is, the estimated Regression Coefficients.
    Example: 
    
    ```{r}
    
    linreg_obj <- linreg$new(formula = Petal.Length, data = iris)
    linreg_obj$print()
    
    ```
    Prints the following:
    
    Coefficients:
    
      (Intercept)  Speciesversicolor   Speciesvirginica  
              1.5                2.8                4.1  

