---
title: "LinearRegVignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{LinearRegVignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LinearRegPackage)
```

This is a package to handle linear regression models. We use it to calculate the various computation required for multiple linear regression and also offer certain functions like plot, print etc.

# Classes offered by the package
1. **linreg**: linreg class contains the following attributes:
    * formula of 'formula' type
    * data of 'data.frame' type
    * est_beta of 'vector' type
    * y_pred of 'matrix' type
    * resid_e of 'matrix' type
    * deg_freed of 'numeric' type
    * resid_var_e of 'matrix' type
    * var_est_beta of 'vector' type
    * t_val_beta of 'matrix' type
    * data_set of 'character' type

    To create an object of class linreg, the formula and data
    attributes must be passed. An example is shown below:


## Methods offered by the class
1. print()

